Are rankings of financial analysts useful to investors?

### 2015-04-01 doc/paper/paper-knitr-APS.Rnw
Include both sets in the paper

<<load.data,echo=F,warning=FALSE,message=FALSE>>=
strategies <- c('true','recent','all-time')
setwd('~/Dropbox/workspace/Projects/BL-strategies')
library(reshape2)
library(descr)
library(data.table)
library(ggplot2)
library(stringr)
library(zoo)
library(xtable)
library(abind)
library(PerformanceAnalytics)
load('cache/q.data.RData')
load('cache/final.bl.RData')
load('cache/market.set.RData')
load('cache/example.dt.RData')
source('lib/aux.functions.R')
#library(ProjectTemplate)
#load.project()
###ADD NAs for the case of no ranking ( if NA, no raking)
trunk.percent <- 0.05
stocks <- unique(market.set[,Stock])
#q.data[,quantile(b.view,c(trunk.percent,1-trunk.percent),na.rm=T)]
q.data.full <- setkey(q.data[,':='(year=format(s.Date,'%Y'))],Stock)

@@

core.dt <- na.omit(q.data)[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)]

#pt.contin.dt <- unique(core.dt[,cont.rank:=.N>8,by=.(q.id,Stock)][(cont.rank)],by=c('q.id','Broker','Stock'))
quarters <- data.table(q.id=core.dt[order(q.id)][,unique(q.id)])

@@

brok.full.stat.pt <- rbind(setkey(na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=year],year),setnames(cbind('Total',na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N))]),1,'year'))

@@

periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')

sel.s <- 'same'

test.a[,'true','CONS',,] <- NA
bl.results['CONS','true',,] <- NA
periods.array[,'CONS','true',,,] <- NA

@@

For the consensus strategy, we use median of expected returns for a particular stock $i$:
\begin{equation}
\label{consq}
Q_{cons,i}= \median \left\{r_{j,i}\right\}
%\frac{1}{N} \sum_{j=1}^{N} r_{j,i}
\end{equation}
%$N$ is the number of analysts with a valid TP report and
where $r_{j,i}=TP_{j,i}/P_{i}-1$  is the last known analyst's $j$ expected return computed using the analyst price target $TP_{j,i}$ and stock price $P_{i}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement. This is done to avoid any information leakage around new TP announcement day \citep{bonini2010}}.

@@

Formalizing information sets considered are: 
\begin{itemize}
\item  the \tr{} set%-- a perfect foresight information:
\begin{equation}
\label{q:true}
\widehat{Q_{rank,i,t}}=Q_{rank,i,t}
\end{equation}
% 
\item  the \naive{} set % -- $t-$ information:
\begin{equation}
\label{q:naive}
\widehat{Q_{rank,i,t}}=Q_{rank,i,t-1}
\end{equation}
% 
\item  the \default{}  set%-- the entire history of analysts performance:
%\begin{itemize}
%\item ranking based views:
\begin{equation}
\label{q:default}
\widehat{Q_{rank,i,t}} = \frac{1}{T-1} \sum_{t=1}^{T-1} Q_{rank,i,t}
\end{equation}
%\item consensus based views:
%\begin{equation}
%\label{default.cons}
%\widehat{consQ_{t,i}} = \frac{1}{T} \sum_{T=1}^{T-1} consQ_{t,i}
%\end{equation}
%\end{itemize}
\end{itemize}
where  $Q_{rank,i,.}$ is the smart estimate for stock $i$ (eq. \ref{rankq}). For the case of consensus based expected returns ($Q_{cons,i}), the \tr{} information set is not applicable as analysts have equal weights.

@@

The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=.(Broker)][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks. To implement the EPS ranking, we require that a stock had at least three brokers per quarter. In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters). Our sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks. Finally, we consider stocks that have both EPS and TP forecasts in a given quarter. The total number of stocks in our sample, thus, is \Sexpr{pt.rank.views[,.N,by=.(type,Stock)][type==sel.s,.N,by=type][,N]} stocks.

%The total number of observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.

@@

Table \ref{tab:view-stat} present the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
%Panel A shows the expected returns based on the analysts consensus and Panel B and C are based on the smart estimates (TP and EPS).

@@

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \naive{} and \default{} information sets are, respectively, \Sexpr{test.a['Total',,'CONS','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'CONS','mean',sel.s][[3]]*100}\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{test.a['Total',,'PT','mean',sel.s][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean',sel.s][[3]]*100}\%). Panel C shows the EPS based weighted expected returns averages (\Sexpr{test.a['Total',,'EPS','mean',sel.s][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean',sel.s][[3]]*100}\%).

@@

The passive strategy generates an annualized cumulative return of \Sexpr{bl.results['Market',1,1,sel.s]}\% with a Sharpe Ratio  of \Sexpr{bl.results['Market',1,'ann.sr',sel.s]} over the period 1999-2001. The average number of stocks held per quarter was \Sexpr{bl.results['Market',1,'meanViews',sel.s]} and the turnover ratio was \Sexpr{bl.results['Market',1,'Ave.TO',sel.s]}, which reflects solely the inclusion and deletions  of the S\&P 500 constituent list.

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['TP',1,1,sel.s]}\%, \Sexpr{bl.results['EPS',1,1,sel.s]}\%. All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,sel.s]}\%). The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be. In any case, the results suggest that the advice of analysts, as a group, is valuable. 
%Yet, the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr',sel.s]} against \Sexpr{ bl.results['EPS',1,'ann.sr',sel.s]} and \Sexpr{ bl.results['Market',1,'ann.sr',sel.s]}, respectively for the \textit{EPS}and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

\subsection{Feasible strategies}
Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set. As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,sel.s]}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1,sel.s]}\%,  \Sexpr{bl.results['CONS',2,1,sel.s]}\%, \Sexpr{bl.results['EPS',2,1,sel.s]}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies. Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns. The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr',sel.s]} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr',sel.s]} and \Sexpr{bl.results['EPS',2,'ann.sr',sel.s]} respectively). The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.

Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1,sel.s]}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1,sel.s]}\% and \Sexpr{bl.results['EPS',3,1,sel.s]}\% respectively). The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

@@

<<desc-rank-pt-t1,echo=F,results='asis'>>=
tab.r <- round(cbind(pt.cont.tab[,,sel.s,'t'],Total=apply(pt.cont.tab[,,1,1],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)

tab.r <- round(cbind(pt.cont.tab[,,sel.s,'t+4'],Total=apply(pt.cont.tab[,,1,2],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
&&$top$&$middle$&$bottom$&Sum\\
<<desc-rank-eps-t1,echo=F,results='asis'>>=
tab.r <- round(cbind(eps.cont.tab[,,sel.s,'t'],Total=apply(eps.cont.tab[,,1,1],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
tab.r <- round(cbind(eps.cont.tab[,,sel.s,'t+4'],Total=apply(eps.cont.tab[,,1,2],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
& Mean (in \%)&Median (in \%)&Std.dev\\
%&all&same&all&same&all&same\\
\midrule
<<desc-q-cons,echo=F,results='asis'>>=
test.a[,,,1:2,sel.s] <- test.a[,,,1:2,sel.s]*100
dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
print(xtable(acast(melt(test.a[12,1:3,'CONS',1:3,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \midrule
<<desc-q-naive,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(acast(melt(test.a[12,,'PT',1:3,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{c}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
  \end{tabularx}

\begin{tabularx}{\linewidth}{r*{4}{Y}}
<<desc-q-eps,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[12,,'EPS',1:3,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{c}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
  \end{table}

@@

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Year&\textit{CONS}& \textit{TP} &\textit{EPS}\\
%&all&same&all&same&all&same\\
<<stocks-true,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[,1,c(1,3,2),4,sel.s]),Var1~Var2,value.var='value'),display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{4}{Y}}
<<stocks-naive,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[,2,c(1,3,2),4,sel.s]),Var1~Var2,value.var='value'),display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{4}{Y}}
<<stocks-def,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[,3,c(1,3,2),4,sel.s]),Var1~Var2,value.var='value'),display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

@@

#p.cum.ret <-
ggplot(final.bl[type==sel.s],aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
#
@

>>>>

<<load.data,echo=F,warning=FALSE,message=FALSE>>=
strategies <- c('true','recent','all-time')
setwd('~/Dropbox/workspace/Projects/BL-strategies')
library(reshape2)
library(descr)
library(data.table)
library(ggplot2)
library(stringr)
library(zoo)
library(xtable)
library(abind)
library(PerformanceAnalytics)
load('cache/q.data.RData')
load('cache/core.dt.RData')
load('cache/final.bl.RData')
load('cache/market.set.RData')
load('cache/example.dt.RData')
source('lib/aux.functions.R')
#library(ProjectTemplate)
#load.project()
###ADD NAs for the case of no ranking ( if NA, no raking)
trunk.percent <- 0.05
stocks <- unique(market.set[,Stock])
#q.data[,quantile(b.view,c(trunk.percent,1-trunk.percent),na.rm=T)]
q.data.full <- setkey(q.data[,':='(year=format(s.Date,'%Y'))],Stock)

@@

#core.dt <- na.omit(q.data)[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)]

#core.dt <- core.dt[,year:=format(q.id,'%Y')]
#pt.contin.dt <- unique(core.dt[,cont.rank:=.N>8,by=.(q.id,Stock)][(cont.rank)],by=c('q.id','Broker','Stock'))
quarters <- data.table(q.id=core.dt[order(q.id)][,unique(q.id)])

@@

brok.full.stat.pt <- rbind(setkey(core.dt[,.N,by=.(Stock,q.id,year,type)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=.(year,type)],year),setnames(cbind('Total',(core.dt)[,.N,by=.(Stock,q.id,year,type)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=type]),1,'year'))

@@

periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')
periods.array[,'CONS','true',,,] <- NA

@@

For the consensus strategy, we use median of expected returns for a particular stock $i$:
\begin{equation}
\label{consq}
Q_{cons,i}= \median \left\{r_{j,i}\right\}
%\frac{1}{N} \sum_{j=1}^{N} r_{j,i}
\end{equation}
%$N$ is the number of analysts with a valid TP report and
where $r_{j,i}=TP_{j,i}/P_{i}-1$  is analyst's $j$ expected return computed using the analyst price target $TP_{j,i}$ and stock price $P_{i}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement. This is done to avoid any information leakage around new TP announcement day \citep{bonini2010}}.

@@

Formalizing information sets considered are: 
\begin{itemize}
\item  the \tr{} set%-- a perfect foresight information:
\begin{equation}
\label{q:true}
\widehat{Q_{.,t}}=Q_{.,t}
\end{equation}

\item  the \naive{} set % -- $t-$ information:
\begin{equation}
\label{q:naive}
\widehat{Q_{.,t}}=Q_{.,t-1}
\end{equation}

\item  the \default{}  set%-- the entire history of analysts performance:
%\begin{itemize}
%\item ranking based views:
\begin{equation}
\label{q:default}
\widehat{Q_{.,t}} = \frac{1}{T} \sum_{t=1}^{T} Q_{.,t}
\end{equation}
%\item consensus based views:
%\begin{equation}
%\label{default.cons}
%\widehat{consQ_{t,i}} = \frac{1}{T} \sum_{T=1}^{T-1} consQ_{t,i}
%\end{equation}
%\end{itemize}
\end{itemize}
where the $.$ subscript corresponds to either $Q_{cons,i}$ (eq. \ref{consq}) or $Q_{rank,i}$ (eq. \ref{rankq}), i.e. this is consensus or smart estimate.

@@

The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=.(Broker)][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks. To implement the EPS ranking, we require that a stock had at least three brokers per quarter. In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters). Our final sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks. The total number of observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.

@@

Tables \ref{tab:view-stat} present the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
%Panel A shows the expected returns based on the analysts consensus and Panel B and C are based on the smart estimates (TP and EPS).

@@

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, \Sexpr{test.a['Total',,'CONS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'CONS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'CONS','mean','all'][[3]]*100}\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{test.a['Total',,'PT','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','all'][[3]]*100}\%). Panel C shows the EPS based weighted expected returns averages (\Sexpr{test.a['Total',,'EPS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','all'][[3]]*100}\%).

@@

The passive strategy generates an annualized cumulative return of \Sexpr{bl.results['Market',1,1,'all']}\% with a Sharpe Ratio  of \Sexpr{bl.results['Market',1,'ann.sr','all']} over the period 1999-2001. The average number of stocks held per quarter was \Sexpr{bl.results['Market',1,'meanViews','all']} and the turnover ratio was \Sexpr{bl.results['Market',1,'Ave.TO','all']}, which reflects solely the inclusion and deletions  of the S\&P 500 constituent list.

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['CONS',1,1,'all']}\%, \Sexpr{bl.results['TP',1,1,'all']}\%, \Sexpr{bl.results['EPS',1,1,'all']}\%. All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,'all']}\%). The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be. In any case, the results suggest that the advice of analysts, as a group, is valuable. 
%Yet, the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr','all']} against \Sexpr{ bl.results['CONS',1,'ann.sr','all']}, \Sexpr{ bl.results['EPS',1,'ann.sr','all']}, and \Sexpr{ bl.results['Market',1,'ann.sr','all']}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

\subsection{Feasible strategies}
Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set. As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,'all']}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1,'all']}\%,  \Sexpr{bl.results['CONS',2,1,'all']}\%, \Sexpr{bl.results['EPS',2,1,'all']}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies. Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns. The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr','all']} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr','all']} and \Sexpr{bl.results['EPS',2,'ann.sr','all']} respectively). The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.

Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1,'all']}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1,'all']}\% and \Sexpr{bl.results['EPS',3,1,'all']}\% respectively). The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

@@

<<desc-rank-pt-t1,echo=F,results='asis'>>=
tab.r <- round(cbind(pt.cont.tab[,,'all','t'],Total=apply(pt.cont.tab[,,1,1],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)

tab.r <- round(cbind(pt.cont.tab[,,'all','t+4'],Total=apply(pt.cont.tab[,,1,2],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
&&$top$&$middle$&$bottom$&Sum\\
<<desc-rank-eps-t1,echo=F,results='asis'>>=
tab.r <- round(cbind(eps.cont.tab[,,'all','t'],Total=apply(eps.cont.tab[,,1,1],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
tab.r <- round(cbind(eps.cont.tab[,,'all','t+4'],Total=apply(eps.cont.tab[,,1,2],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
&all&same&all&same&all&same\\
\midrule
<<desc-q-cons,echo=F,results='asis'>>=
test.a[,,,1:2,] <- test.a[,,,1:2,]*100
dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
print(xtable(acast(melt(test.a[12,1:3,'CONS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \midrule
<<desc-q-naive,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(acast(melt(test.a[12,,'PT',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
  \end{tabularx}

\begin{tabularx}{\linewidth}{r*{7}{Y}}
<<desc-q-eps,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[12,,'EPS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
  \end{table}

@@

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
&all&same&all&same&all&same\\
<<stocks-true,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[,1,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{7}{Y}}
<<stocks-naive,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[,2,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{7}{Y}}
<<stocks-def,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[,3,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

@@

#p.cum.ret <-
ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(type~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
#
@
